\chapter{Documentation of AI Tool Usage}
\label{app:ai-usage}

This appendix documents the use of artificial intelligence tools in
preparing this thesis, as required by the university.

% ─────────────────────────────────────────────────────────────────────────────
\section*{Extraction Validation (Section~\ref{ssec:text_coverage})}

\paragraph{Tool.} Google Gemini~2.5~Flash (accessed via the OpenAI-compatible
Gemini API endpoint), with temperature set to~0 for deterministic output.

\paragraph{Purpose.} An independent, automated quality audit of the
SEC~10-K section extraction pipeline.  The model evaluated 200~extracted
sections (100~Item~1A, 100~Item~7) against a structured five-criterion
rubric (correct section, start boundary, end boundary, content quality,
completeness) on a three-level scale (Pass / Minor / Fail).

\paragraph{Contribution and verification.}
The evaluation rubric, sampling strategy, prompt design, and statistical
analysis (Wilson confidence intervals) were all designed by the author.
The model's only role was applying the rubric to each extracted section.
All Fail verdicts were manually spot-checked against the original SEC
filings and confirmed to be correct.  Results are in
Table~\ref{tab:ai_validation}.

% ─────────────────────────────────────────────────────────────────────────────
\section*{Code Development}

\paragraph{Tool.} AI-powered code completion (integrated in VS Code).

\paragraph{Purpose.} Code completion and boilerplate generation during the
development of data-pipeline scripts (\texttt{scripts/} directory).

\paragraph{Contribution and verification.}
All generated code was reviewed, tested, and modified by the author.
The overall architecture, variable definitions, and analytical choices
are the author's own.

% ─────────────────────────────────────────────────────────────────────────────
\section*{Writing Assistance}

\paragraph{Tool.} AI-powered writing assistant (integrated in VS Code).

\paragraph{Purpose.} Grammar and style suggestions for English-language
prose in the thesis text.

\paragraph{Contribution and verification.}
All substantive content, argumentation, and interpretation are the
author's own.  The tool was used only for language polishing; every
suggestion was reviewed before acceptance.
