%%% Single-sided print version:
\documentclass[11pt,a4paper]{report}
\usepackage[top=25mm,bottom=25mm,right=25mm,left=30mm,head=12.5mm,foot=12.5mm]{geometry}
\let\openright=\clearpage

%%% Double-sided print version (uncomment if needed):
%\documentclass[11pt,a4paper,twoside,openright]{report}
%\usepackage[top=25mm,bottom=25mm,right=25mm,left=30mm,head=12.5mm,foot=12.5mm]{geometry}
%\let\openright=\cleardoublepage

%%% VARIABLE DEFINITIONS
\def\TypPrace{BP}                % bachelor thesis
\def\Jazyk{eng}                  % english

%%% Package definitions and macros (see inside file)
\input{makra}

%%% Thesis title (exact according to assignment)
\def\NazevPrace{Textual-Financial Divergence and Stock Return Volatility: Evidence from U.S. Corporate Filings}

%%% Author's name
\def\AutorPrace{Šimon Slanský}

%%% Year and month of submission
\def\DatumOdevzdani{January 2027}

%%% Supervisor
\def\Vedouci{prof. RNDr. Ing. Michal Černý, Ph.D.}

%%% Consultant (leave empty if none)
\def\Konzultant{}

%%% Study programme
\def\StudijniProgram{Data Analytics}

%%% Specialization (leave empty if none)
\def\Specializace{}

%%% Acknowledgments
\def\Podekovani{%
% TODO: Acknowledge supervisor, family, etc.
}

%%% Abstract in Czech (required even for English theses)
\def\Abstrakt{%
Výroční zprávy amerických firem (formulář 10-K) obsahují jak auditovaná
finanční data, tak rozsáhlé textové části psané vedením společnosti.
Většina empirických modelů však tyto dva informační kanály zkoumá
odděleně.
%
Tato práce zkoumá, zda nesoulad mezi směrem změny manažerského jazyka
a~směrem souběžné finanční změny---označovaný jako
\emph{textuálně-finanční divergence}---předpovídá budoucí volatilitu
akciových výnosů.
%
Na nevyváženém panelu 537 velkých amerických firem za fiskální
roky 2010--2024 (6\,299 pozorování v~regresním vzorku) extrahuji sekce Rizikové faktory
(Item~1A) a~Diskusi vedení (Item~7) z~každé zprávy 10-K pomocí vlastního
parseru SEC EDGAR.  Meziroční změny sentimentu, hustoty rizikových slov
a~textové podobnosti jsou kombinovány se standardními finančními
kontrolními proměnnými v~OLS regresích s~absorbovanými odvětvovými
a~ročními fixními efekty.
%
Výsledky základního finančního modelu ukazují, že zpožděná volatilita,
velikost firmy a~ziskovost společně vysvětlují 65,4\,\% průřezové variace
v~anualizované volatilitě po zveřejnění zprávy.  Zpožděná volatilita je
nejsilnějším prediktorem (koeficient 0,55; $t=20{,}7$), ROA má silně
negativní vliv ($-0,22$; $t=-7{,}9$) a~růst aktiv vstupuje kladně
($+0,03$; $t=3{,}1$).  Výsledky textové analýzy a~modelu divergence budou
doplněny.
%
Pokud se divergence potvrdí jako významný prediktor, mohla by sloužit jako
nový signál pro identifikaci firem, jejichž narativní zveřejnění si
zaslouží pozornější posouzení, s~implikacemi pro řízení rizik
a~regulatorní dohled nad kvalitou firemního výkaznictví.
}

%%% Abstract in English
\def\AbstraktEN{%
Corporate 10-K filings consist of both audited financial data and extensive
narrative sections written by management, yet most empirical models work with
these two information channels separately. Whether the \emph{interaction}
between narrative language and reported financial metrics has any
additional information about firm-level risk is still largely unexplored.
%
This thesis asks whether a mismatch between the direction of change in
managerial language and the direction of concurrent financial
change---called \emph{textual-financial divergence}---predicts future
stock return volatility.
%
I build an unbalanced panel of 537 large U.S.\ companies over
fiscal years 2010--2024 (6{,}299 firm-year observations in the regression
sample) and extract the Risk Factors (Item~1A) and Management's Discussion
(Item~7) sections from each 10-K filing using a custom SEC EDGAR parser.
Year-over-year changes in sentiment, risk-word density, and textual
similarity are computed and combined with standard financial controls in
absorbing OLS regressions with industry and year fixed effects.
%
Results from the financial baseline model show that lagged volatility,
firm size, and profitability together explain 65.4\,\% of the
cross-sectional variation in post-filing annualised volatility.
Lagged volatility is the strongest predictor (coefficient 0.55,
$t=20.7$), while ROA has a strong negative effect ($-0.22$, $t=-7.9$)
and asset growth enters positively ($+0.03$, $t=3.1$). Textual results
and the divergence model will be added in subsequent revisions.
%
If divergence proves to be a significant predictor, it could serve as a
new signal for identifying firms whose narrative disclosures warrant closer
scrutiny, with implications for risk management and regulatory oversight
of corporate-reporting quality.
}

%%% Keywords in Czech
\def\KlicovaSlova{textová analýza, 10-K výkazy, SEC EDGAR, volatilita,
informační nejistota, narativní divergence, sentiment, panelová data,
firemní zprávy}

%%% Keywords in English
\def\KlicovaSlovaEN{textual analysis, 10-K filings, SEC EDGAR, volatility,
information uncertainty, narrative divergence, sentiment, panel data,
corporate disclosures}

%%% Title page and mandatory information pages
%% Compile all chapters
% \includeonly{zacatek,chapters/05_results}
\begin{document}
\include{zacatek}

%%% Table of contents
\setcounter{tocdepth}{2}
\tableofcontents

%%% List of figures (optional — use if >20 figures)
%\openright
%\listoffigures

%%% List of tables (optional — use if >20 tables)
%\clearpage
%\listoftables

%%% List of abbreviations
\include{zkratky}

\pagestyle{fancyx}
%%% Individual chapters
{%
\pagestyle{plain}
\include{uvod}
}
\include{chapters/02_literature_review}
\include{chapters/03_data}
\include{chapters/04_methodology}
\include{chapters/05_results}
\include{chapters/06_robustness}
{%
\pagestyle{plain}
\include{zaver}
}

%%% Bibliography
\include{literatura}

%%% Appendices
\part*{\Prilohy\thispagestyle{empty}}
\appendix
\include{app01}
\include{app02}

\end{document}
