% =============================================================================
\chapter{Data}
\label{ch:data}
% =============================================================================

% TODO: Structure
%
% \section{Sample Selection}
% - Universe: top ~1,000 U.S. companies by market cap from SEC EDGAR
% - Filters: operating entities only, exclude SIC 6000--6999 (financials)
% - Final sample: ~600 non-financial firms, 2010--2025
% - Table~\ref{tab:sample}: industry distribution, FYE month distribution
%
% \section{Data Sources}
% \subsection{SEC EDGAR}
% - XBRL Company Facts API for financial statements (10-K)
% - Full-text filings for textual analysis (Item 7 MD\&A, Item 1A Risk Factors)
%
% \subsection{Stock Market Data}
% - Source: yfinance (adjusted close prices)
% - Volatility: annualised std of daily log returns over 365-day post-filing window
%
% \section{Financial Variables}
% - Raw XBRL metrics: total\_assets, net\_income, operating\_income,
%   operating\_cash\_flow, eps\_diluted, etc.
% - Derived ratios: log\_total\_assets, leverage, ROA, asset\_growth,
%   current\_ratio, accruals, ocf\_to\_assets, operating\_roa
% - Winsorisation at 1\%/99\%
%
% \section{Textual Variables}
% - $\Delta$Sentiment: YoY change in Loughran--McDonald net tone (Item 7)
% - $\Delta$Risk: YoY change in risk-word frequency (Item 1A)
% - TextSim: cosine similarity of consecutive filings
%
% \section{Divergence Measure Construction}
% - Financial trajectory: $\Delta$ROA = ROA$_t$ $-$ ROA$_{t-1}$
% - Narrative trajectory: $\Delta$Sentiment = Sent$_t$ $-$ Sent$_{t-1}$
% - Continuous: Divergence = $\Delta$Sentiment $-$ $\lambda \cdot \Delta$ROA
% - Binary: DivDummy = 1 if sign($\Delta$Sentiment) $\neq$ sign($\Delta$ROA)
%
% \section{Dependent Variable}
% - Primary: annualised volatility (std of daily log returns $\times \sqrt{252}$)
%   over 365-day post-filing window
% - Robustness: post-filing log stock return
%
% \section{Panel Data Construction}
% - Annual panel: ~9,000 firm-years
% - Unbalanced panel, fiscal year-end alignment
%
% \section{Descriptive Statistics}
% - Summary statistics (Table~\ref{tab:desc_stats})
% - Correlation matrix (Table~\ref{tab:correlations})


% ─────────────────────────────────────────────────────────────────────────────
\section{Sample Selection}
\label{sec:sample_selection}
% ─────────────────────────────────────────────────────────────────────────────

The starting universe consists of the 1{,}000 largest U.S.\ public
companies by market capitalisation as listed in the SEC EDGAR
company-tickers file.  We apply three filters.  First, we retain only
entities classified as ``operating'' by the SEC, which removes
exchange-traded funds, closed-end funds, blank-cheque companies, and
shell entities.  Second, we exclude firms in SIC codes~6000--6999
(finance, insurance, and real estate), whose financial-statement
structure is incomparable with that of industrial firms---a standard
restriction in the accruals and earnings-quality literature
\parencite{sloan1996,francis2005}.  Third, we require at least five
years of machine-readable XBRL data from 10-K filings and 90\% valid
stock-return coverage, which ensures sufficient within-firm variation
for fixed-effects estimation.  The resulting sample comprises
approximately 540 non-financial firms observed over fiscal years
2010--2024, yielding roughly 6{,}400 firm-year observations.

\paragraph{Sample size.}
The panel is deliberately restricted to large, liquid firms rather
than the full EDGAR universe.  Three considerations motivate this
choice.  First, our identification relies on firm fixed effects with
standard errors clustered at the firm level.  As
\textcite{petersen2009} demonstrates, the precision of cluster-robust
inference depends on the number of clusters---here approximately
540---not on the total number of observations; 540~clusters are well
above the thresholds at which cluster-robust standard errors perform
reliably.  Second, the textual-analysis component of the study
requires downloading, parsing, and scoring the full text of every 10-K
filing in the sample.  Extending the universe to several thousand
firms would multiply this computational burden without proportional
gains in statistical power.  Third, smaller firms tend to have shorter
XBRL histories (mandatory electronic filing was phased in by size),
higher rates of tagging errors, and thinner stock-market trading,
all of which would increase measurement noise in financial ratios and
return-based outcome variables.

The resulting sample size is comparable to prior work that combines
textual and financial analysis of annual filings.
\textcite{campbell2014} analyse approximately 7{,}000 firm-years of
risk-factor disclosures drawn from large U.S.\ firms;
\textcite{loughran2011} use a broader universe of roughly
50{,}000 firm-years, but their research question---validating a
sentiment dictionary---requires maximal cross-sectional coverage,
whereas our divergence measure is estimated within firms over time.


% ─────────────────────────────────────────────────────────────────────────────
\section{Filing Frequency}
\label{sec:annual_vs_quarterly}
% ─────────────────────────────────────────────────────────────────────────────

Before proceeding to variable construction, a brief note on why this study
works with annual 10-K filings rather than quarterly 10-Q reports is in order.
Although quarterly data would roughly triple the sample, three practical
obstacles---documented in Tables~\ref{tab:xbrl_coverage}--\ref{tab:text_availability}---ruled
out that path.

\paragraph{Financial data gaps in Q4.}
10-Q filings cover only Q1 through Q3; the fourth quarter must therefore be
backed out as the residual between the annual figure and the three preceding
quarters. Table~\ref{tab:q4_reliability} shows that complete Q1--Q3 XBRL
data exist for roughly 80\% of firm-years in net income and operating income,
but for only 7\% in operating cash flow---because most firms report
cumulative year-to-date cash flows rather than standalone quarterly amounts.
Where both an explicit Q4 fact and the implied residual can be compared,
about 11\% of observations diverge by more than 1\% of the annual total.
Because accruals depend directly on operating cash flow, the quarterly route
would have made hypothesis~H3 untestable.

\input{tables/q4_reliability}

\paragraph{Missing risk-factor text in 10-Q.}
SEC Regulation S-K requires firms to update risk factors in quarterly filings
only when ``material changes'' have occurred since the last 10-K.  Practically
speaking, just over half the 10-Q filings we sampled (15 firms, 90 filings)
contained a substantive risk-factor section; the rest reduced to a one-sentence
reference back to the annual report (Table~\ref{tab:text_availability}).
This pattern held across sectors---technology, healthcare, consumer goods,
energy---with only occasional exceptions.  Constructing $\Delta$Risk, which
enters both H1 and H2, is therefore not feasible at a quarterly frequency.

\input{tables/text_availability}

\paragraph{Chosen frequency.}
On these grounds---and in line with prior textual-analysis work based on
10-K filings \parencite{loughran2011,li2008,blankespoor2020}---we adopt an
annual panel. The XBRL coverage comparison (Table~\ref{tab:xbrl_coverage})
and a consolidated summary (Table~\ref{tab:annual_vs_quarterly}) are
included in Appendix~\ref{app:diagnostics} for completeness.

% Full diagnostic tables deferred to appendix:
% \input{tables/xbrl_coverage}       → Appendix
% \input{tables/annual_vs_quarterly} → Appendix


% ─────────────────────────────────────────────────────────────────────────────
\section{XBRL Tag Consistency}
\label{sec:xbrl_tags}
% ─────────────────────────────────────────────────────────────────────────────

A practical challenge of the XBRL Company Facts API is that a single
accounting concept may be reported under alternative US-GAAP taxonomy tags.
For instance, operating cash flow appears as either
\texttt{NetCashProvided\-ByUsed\-InOperating\-Activities} (total, including
discontinued operations) or
\texttt{...ContinuingOperations} (continuing operations only).
Net income may be tagged as \texttt{NetIncomeLoss}, \texttt{ProfitLoss},
or \texttt{IncomeLossFrom\-ContinuingOperations}.
Stockholders' equity can include or exclude the non-controlling interest.
Although the concepts overlap substantially, they are not identical:
combining them within a single firm's time series could introduce
artificial breaks, while selecting one tag globally would discard firms
that consistently report under the alternative.

We resolve this with a two-tier \emph{tag-harmonisation} procedure.

\paragraph{Equivalence groups.}
For tag pairs that differ only in taxonomy version---not in economic
content---we allow both tags to coexist within a firm's time series.
Specifically, the two operating-cash-flow tags and the pair
\texttt{NetIncomeLoss}/\texttt{ProfitLoss} are each treated as
interchangeable.  The third net-income variant,
\texttt{IncomeLossFromContinuingOperations}, is \emph{not} included
because it deliberately excludes discontinued operations and can differ
materially.

To verify this classification empirically, we queried the SEC EDGAR
Company~Facts API for all 550 sample firms and identified 6{,}113
firm-year periods in which both tags of a pair were reported
simultaneously.  For operating cash flow, 53.5\% of these 1{,}352 overlap
observations were numerically identical and the median difference
scaled by total assets was 0.000~pp; even at the 90th~percentile the
bias reached only 1.5~pp of total assets.  For net income, 25.5\% of
the 4{,}761 overlaps were exact matches; the median bias on ROA was
0.033~pp, with 92.5\% of observations below 1.0~pp.  Cases with
non-trivial differences correspond almost exclusively to firms with
material non-controlling interests (e.g.\ master limited partnerships),
which our priority rule already resolves by preferring the
parent-company tag when both are available.

\paragraph{Per-firm tag locking.}
For metrics whose alternative tags \emph{are} economically distinct
(stockholders' equity with vs.\ without NCI; \texttt{IncomeLoss\-From\-%
ContinuingOperations} vs.\ \texttt{NetIncomeLoss}), we apply strict
per-firm tag locking:\ the tag each firm uses in the most fiscal years
is retained, and values from non-dominant tags are set to missing.
This ensures within-firm time-series consistency---the critical
requirement for panel regressions that identify effects from within-firm
variation.

The combination of equivalence groups and per-firm locking raises the
complete-case rate for the six regression controls (\textit{roa},
\textit{accruals}, \textit{leverage}, \textit{asset\_growth},
\textit{current\_ratio}, \textit{log\_total\_assets}) from 78.9\% to
92.7\% of firm-year observations, recovering 988 accruals values,
828 operating-cash-flow values, and 292 net-income values that would
otherwise be discarded.

\paragraph{Residual limitation.}
The accruals ratio $(\text{NI} - \text{OCF}) / \text{TA}$ requires
that NI and OCF measure income and cash flow at the \emph{same}
scope.  Our procedure enforces consistency within each metric but not
across metrics: approximately 4\% of firms lock to the
continuing-operations OCF tag while using total net income.  We
consider this acceptable:\ the affected share is small, winsorisation
at the 1st and 99th percentiles clips extreme values, and the same
cross-tag mismatch is present in comparable large-scale XBRL studies
\parencite{chen2019}.

Per-firm tag choices and the overlap diagnostic are reported in
Appendix~\ref{app:variables}
(Table~\ref{tab:tag_provenance}).


% ─────────────────────────────────────────────────────────────────────────────
\section{Textual Data Extraction}
\label{sec:text_extraction}
% ─────────────────────────────────────────────────────────────────────────────

Several hypotheses of this study rely on the narrative content of 10-K
filings---specifically Item~1A \emph{Risk Factors} and Item~7
\emph{Management's Discussion and Analysis of Financial Condition and
Results of Operations} (MD\&A).  This section describes how those
sections are identified and extracted from the raw HTML filings
available on SEC EDGAR.

\subsection{Data Source and Filing Population}
\label{ssec:text_source}

All filings are retrieved directly from the SEC EDGAR Archives using
the Submissions~API, which maps each company's Central Index Key (CIK)
to the set of primary documents associated with its 10-K filings.
From the panel of approximately 6{,}700 firm-year observations, we
exclude 10-K/A amendment filings.  Amendments typically consist of a
cover page and a single restated exhibit; they do not contain the full
narrative sections of the original 10-K.  The financial data for
amended fiscal years are retained, as the XBRL extraction pipeline
already selects the amended figures when available
(Section~\ref{sec:xbrl_tags}).  Our extraction thus targets exclusively
original 10-K filings.

\subsection{Section Identification}
\label{ssec:section_id}

Unlike structured XBRL data, the narrative portions of 10-K filings
are embedded in HTML with no standardised tagging.  The raw filing
may span tens of thousands of lines of HTML, with section headers
rendered through a variety of styling conventions---CSS bold, explicit
\texttt{<font>} tags, inline uppercase text, or table-based layouts---and
interleaved with a table of contents (TOC), running headers, and
inline cross-references (e.g.\ ``see Item~1A'').  These
characteristics make na{\"i}ve keyword search on plain text unreliable,
as it conflates TOC entries, page headers, and inline mentions with
the actual section boundary \parencite{dyer2017}.

We implement an HTML-aware extraction procedure that operates in
four stages:

\begin{enumerate}
  \item \textbf{Header detection.}  The HTML DOM is traversed at the
    block level (\texttt{<p>}, \texttt{<div>}, \texttt{<td>},
    \texttt{<h1>}--\texttt{<h6>}) and each element is tested against
    a set of regex patterns corresponding to the target sections
    (e.g.\ \texttt{Item\textbackslash s+1[\textbackslash s.]*A} for
    Item~1A).  A candidate is accepted only if it satisfies at least
    one formatting criterion: bold styling (CSS \texttt{font-weight:
    bold} or \texttt{700}), ALL-CAPS text, or large font size
    ($\geq$12\,pt via CSS or legacy \texttt{<font size$\geq$3>}
    attribute).  This requirement filters out inline cross-references,
    which appear in body-text paragraphs with no special formatting.
    Additionally, elements containing visible hyperlinks (an
    \texttt{<a>} tag with an \texttt{href} attribute) are rejected, as
    these correspond to TOC entries linking to the real section.

  \item \textbf{Position marking.}  Each detected header is annotated
    with a unique marker character inserted into the DOM before the
    document is flattened to plain text.  The markers record the
    character offset of every confirmed header in the resulting text
    stream.

  \item \textbf{Candidate selection.}  For each target section, all
    marker positions are filtered by a subtitle keyword check (e.g.\
    ``risk'' for Item~1A, ``management'' or ``discussion'' for
    Item~7) within 150~characters of the marker.  A TOC-cluster
    heuristic then rejects any candidate whose position lies within
    300~characters of two or more headers belonging to different
    items---a pattern characteristic of tables of contents.  Among
    the remaining candidates, the one followed by the longest text
    span before the next section header is selected.

  \item \textbf{Section boundary.}  The section text is defined as
    the content between the selected header and the first occurrence
    of the next expected Item header (Item~1B, 1C, or~2 for
    Item~1A; Item~7A or~8 for Item~7).  Sections shorter than
    200~words are classified as stubs and trigger a fallback
    procedure.
\end{enumerate}

\subsection{Exhibit Fallback}
\label{ssec:exhibit_fallback}

A common practice in 10-K filings---particularly among older filings
and firms that publish a standalone annual report---is to reduce an
Item to a short stub such as ``This information is incorporated by
reference from Exhibit~13.''  When the extracted section contains
fewer than 200~words and the text matches an incorporation-by-reference
pattern, the parser identifies the referenced exhibit number
(defaulting to Exhibit~13, the annual report to shareholders) and
downloads the corresponding HTML document from the filing index.  The
section identification procedure is then reapplied to the exhibit.
Because exhibits frequently omit the formal ``Item~X'' prefix, the
parser also matches title-only patterns (e.g.\ ``Risk Factors'',
``Management's Discussion and Analysis'') as a secondary detection
layer for both the main document and exhibits.

\subsection{Post-Processing}
\label{ssec:text_postprocessing}

The raw text produced by the HTML-to-plain-text conversion retains
several artefacts of the original filing's page layout.  Before any
textual feature is computed, each extracted section passes through a
cleaning step that removes three classes of noise:

\begin{enumerate}
  \item \textbf{Running page headers.}  Many filings embed
    ``\textit{$\langle$page number$\rangle$~Table of Contents}''
    strings at page boundaries.  A regular expression strips any
    line matching a one- to three-digit number followed by
    ``Table of Contents.''
  \item \textbf{Standalone page numbers.}  After removing the full
    header pattern, some filings still contain bare page numbers on
    otherwise empty lines.  These are removed by a second pass that
    deletes any line consisting solely of a one- to three-digit
    integer.
  \item \textbf{Non-breaking spaces.}  HTML \texttt{\&nbsp;} entities
    (Unicode~\texttt{U+00A0}) are replaced with standard spaces to
    ensure consistent tokenisation in downstream word-count and
    dictionary-based measures.
\end{enumerate}

\noindent
The cleaning rules are intentionally conservative: they target only
patterns that cannot plausibly form part of meaningful sentence text
and are applied after section boundaries have already been
resolved---so they do not interfere with header detection.

\subsection{Coverage and Limitations}
\label{ssec:text_coverage}

We validated the extraction pipeline on two samples: the 50~most
recent filings in the panel (fiscal year 2024) and a stratified
random sample of 100~filings spanning all fiscal years 2010--2024
(20~per era).  On the recent sample, the parser successfully
extracted both sections for all 50~filings (100\%).  On the
cross-era sample, 94~of 100~filings yielded both sections.  The
six failures were classified as follows:

\begin{itemize}
  \item Three 10-K/A amendments that passed the initial filter because
    the panel did not yet carry a form-type indicator at the time of
    testing (since corrected);
  \item Two filings whose annual report exhibit was filed as a PDF
    rather than HTML, making it inaccessible to an HTML parser;
  \item One filing (9.3\,MB of HTML) that contained no bold, large-font,
    or uppercase cues whatsoever, rendering header detection infeasible.
\end{itemize}

\noindent
None of these failures is systematic with respect to firm
characteristics.  On the full panel---after excluding amendments---we
expect a coverage rate of approximately 96--97\%, with missing values
treated as NaN in the textual variable construction.

\paragraph{AI-assisted quality audit.}
%
% DESIGN RATIONALE (n = 100 filings / 200 sections):
%   1. Statistical precision: With ~200 evaluated sections and an
%      expected pass rate of ~95%, the Wilson 95% CI half-width is
%      z * sqrt(p*(1-p)/n) ≈ 1.96 * sqrt(0.95*0.05/200) ≈ 3.0 pp,
%      yielding intervals narrow enough for a definitive claim.
%   2. Representativeness: 100 filings = 40 sections per 5-era
%      stratum covers the full filing-format evolution
%      (pre-iXBRL → transition → inline XBRL),
%      sampling ~18% of the 540-firm universe.
%   3. Literature precedent: Manual/AI extraction validation in
%      financial NLP typically uses 50–100 documents
%      (cf. Loughran & McDonald spot checks; Krippendorff recommends
%      ≥ 80 units for reliability testing).
%
To verify not only coverage but also content quality, we conducted an
independent audit using a large language model (Gemini~2.5 Flash,
temperature~$= 0$).  Recent work by \textcite{gilardi2023} demonstrates
that LLM-based annotation matches or exceeds the accuracy of trained
human crowd-workers on text-classification tasks, supporting the use
of a language model as an independent extraction judge.
A~stratified random sample of 100~filings was drawn---40~sections
per era across five strata (2010--2012, 2013--2015, 2016--2018,
2019--2021, 2022--2024)---yielding 200~section-level evaluations
(Item~1A and Item~7 for each filing).
The sample size exceeds the minimum of~80~coding units recommended
by \textcite{krippendorff2019} for content-analysis reliability
testing.  At the observed pass rates, the Wilson~95\,\%
confidence interval half-width does not exceed approximately
3~percentage points \parencite{agresti1998}, providing sufficient
precision for a definitive quality claim.  The 100~filings cover
roughly~18\,\% of the 540-firm panel and span the full evolution of
SEC filing formats.

For each filing, both extracted sections were submitted to the model
in a single prompt together with a structured evaluation rubric.
The model judged each section on five criteria---correct section
identity, start-boundary accuracy, end-boundary accuracy, content
quality (absence of residual HTML tags, page headers, or garbled
data), and completeness (full narrative, not a stub or truncated
fragment)---using a three-level scale: \emph{Pass} (criterion
clearly satisfied), \emph{Minor} (small issue that would not
materially affect NLP analysis), and \emph{Fail} (issue that would
distort results).  We report two aggregate metrics: a strict rate
(only Pass) and a lenient rate (Pass~+~Minor), each accompanied by
Wilson~95\,\% confidence intervals \parencite{agresti1998}.

\begin{table}[htbp]
  \centering
  \small
  \caption{AI-assisted extraction validation results
           ($n = 200$~sections, 100~per section type).}
  \label{tab:ai_validation}
  \begin{tabular}{l r@{/}l r r@{/}l r l}
    \toprule
    Criterion &
      \multicolumn{2}{c}{Strict} & \% &
      \multicolumn{2}{c}{Lenient} & \% &
      95\,\% CI (lenient) \\
    \midrule
    Correct section   & 192 & 200 & 96.0 & 192 & 200 & 96.0 & [92.3\,--\,98.0\,\%] \\
    Start boundary    & 191 & 200 & 95.5 & 193 & 200 & 96.5 & [93.0\,--\,98.3\,\%] \\
    End boundary      & 192 & 200 & 96.0 & 193 & 200 & 96.5 & [93.0\,--\,98.3\,\%] \\
    Content quality   & 191 & 200 & 95.5 & 195 & 200 & 97.5 & [94.3\,--\,98.9\,\%] \\
    Completeness      & 189 & 200 & 94.5 & 191 & 200 & 95.5 & [91.7\,--\,97.6\,\%] \\
    \midrule
    Overall (all five) & 179 & 200 & 89.5 & 187 & 200 & 93.5 & [89.2\,--\,96.2\,\%] \\
    \bottomrule
  \end{tabular}
\end{table}

Table~\ref{tab:ai_validation} reports the results.  On every
individual criterion, the lenient pass rate (Pass~+~Minor) exceeds
95\,\%, confirming that the parser isolates the correct section with
accurate boundaries and yields clean, complete text.  Even under the
strict metric---which counts only an unqualified Pass---rates remain
above 94\,\% on each criterion.  The overall lenient rate across all
five criteria simultaneously is 93.5\,\% (187/200; 95\,\%~CI:
89.2--96.2\,\%).

Of the 13~sections that received at least one Fail, five were
complete extraction failures (empty output) caused by non-standard
HTML layouts or parser recursion limits; four had incorrect section
boundaries (content from an adjacent Item was included); and the
remaining four were flagged solely for low word counts suggesting
potential truncation.  Item~7 extractions perform slightly better
than Item~1A (lenient pass rates of 96\,\% vs.\ 91\,\%),
likely because Item~7 has a cleaner stop boundary (Item~7A or
Item~8), whereas Item~1A occasionally captures text from the
preceding Item~1.

Failures also concentrate in older filings: 5~of the 40~sections
from 2010--2012 were flagged versus only 1~of~40 from 2022--2024,
reflecting the progressive standardisation of SEC filing HTML over
the sample period.  The pattern reinforces that the residual
failures are not systematic with respect to firm characteristics
but rather an artefact of filing-format heterogeneity in the
early XBRL era.

\paragraph{Robustness of the LLM-based audit.}
We use Google Gemini~2.5~Flash (accessed through its
OpenAI-compatible API) with temperature set to~0 to ensure
deterministic evaluation.  Several design choices support the
reliability of this approach.  First, \textcite{gilardi2023}
demonstrate that LLM-based annotation matches or exceeds the
accuracy of trained crowd-workers on text-classification tasks,
providing methodological precedent for using a language model as an
independent judge.  Second, the evaluation rubric is structured with
concrete, verifiable criteria---correct section identity, boundary
accuracy, absence of HTML artefacts, word-count thresholds---that
leave little room for subjective interpretation.  Third, each
judgment involves a single document and a deterministic prompt; the
model does not need to compare across filings or aggregate
statistics.  Fourth, spot-checking the model's Fail verdicts against
manual inspection confirmed agreement in all cases examined (e.g.\
the PH~2015 and FE~2010 empty extractions, the ROP~2019 and PEP~2017
boundary errors).  The combination of a well-defined rubric, zero
temperature, and verifiable failure modes makes the audit
generalisable: a different evaluator---human or model---applying the
same criteria would be expected to reach the same conclusions.

\paragraph{Relation to prior approaches.}
The extraction strategy follows the general methodology described by
\textcite{dyer2017}, who document substantial variation in the HTML
structure of SEC filings and recommend DOM-based parsing over regular
expressions applied to raw text.  Relative to keyword-on-plain-text
approaches used in earlier work
\parencite{li2008,loughran2011,campbell2014}, our procedure avoids
false positives from TOC entries and inline mentions, which
\textcite{dyer2017} identify as a significant source of measurement
error in automated section extraction.  When compared with the
XBRL-tagged textual blocks (e.g.\
\texttt{us-gaap:RiskFactorsTextBlock}), which became available with
Inline XBRL adoption, our method offers broader temporal coverage:
structured textual tags are inconsistently populated before 2018,
whereas the HTML-based approach covers the full 2010--2024 window.
