% =============================================================================
\chapter{Results}
\label{ch:results}
% =============================================================================

% TODO: Structure
%
% \section{Text Model Results (H1)}
% - Coefficients for $\Delta$Sentiment, $\Delta$Risk, TextSim
% - Incremental $R^2$ over baseline
% - Expected: $\Delta$Risk positive, $\Delta$Sentiment negative, TextSim negative?
%
% \section{Divergence Model Results (H2)}
% - Coefficient for Divergence (the key result)
% - Expected: positive — narrative-financial mismatch → higher future vol
% - Incremental $R^2$ over the text model
% - F-test for divergence significance
%
% \section{Accruals Interaction (H3)}
% - Divergence × HighAccrual interaction term
% - Expected: positive — divergence effect concentrates in low-quality firms
%
% \section{Economic Magnitude}
% - Portfolio sorts by divergence quartile → spread in future volatility
% - What does a 1-SD increase in divergence imply for annual vol?


% ─────────────────────────────────────────────────────────────────────────────
\section{Descriptive Statistics}
\label{sec:descriptive}
% ─────────────────────────────────────────────────────────────────────────────

Table~\ref{tab:summary} reports summary statistics for the regression
sample.  The dependent variable, post-filing annualised volatility, has a
mean of roughly 0.33 and a standard deviation of 0.17, reflecting
substantial cross-sectional variation in firm-level risk.  The
interquartile range (0.22 to 0.39) indicates that the distribution is
right-skewed, consistent with occasional spikes during market stress
periods such as 2020.

Lagged volatility has a nearly identical distribution, as expected
for a persistent series.  Firm size, measured as $\ln(\text{Total Assets})$,
ranges from mid-sized (P25~$\approx$~22.1) to large
companies (P75~$\approx$~24.2).  Leverage centres around 0.61 with
moderate dispersion.  ROA has a mean near 0.06, and asset growth
averages roughly 0.12 with a long right tail reflecting acquisitive firms.
Accruals average $-0.05$, suggesting that operating cash flow is generally 
higher than net income, mainly because of non-cash expenses such as 
depreciation and amortisation.

\input{tables/summary_statistics}

Table~\ref{tab:correlation} presents pairwise Pearson correlations.
Volatility and its lag are strongly positively correlated ($r = 0.61$),
confirming persistence.  Firm size is negatively correlated with
volatility ($r \approx -0.32$), consistent with the well-documented
size--risk relation.  ROA also correlates negatively with volatility,
while leverage and asset growth show weaker univariate associations.
Accruals correlate negatively with volatility ($r = -0.19$) and share a
moderate positive correlation with ROA ($r = 0.44$), reflecting the
mechanical link through net income---this overlap motivates including
both in the regression to separate cash-based and accrual-based
profitability effects.
None of the pairwise correlations among the explanatory variables
exceed 0.45 in absolute value, mitigating multicollinearity concerns
(confirmed by variance inflation factors below 1.4 for all regressors).

\input{tables/correlation_matrix}


% ─────────────────────────────────────────────────────────────────────────────
\section{Baseline: Financial Determinants of Volatility}
\label{sec:baseline}
% ─────────────────────────────────────────────────────────────────────────────

Before introducing textual variables, we establish the predictive
power of standard financial determinants over future stock return
volatility.  Table~\ref{tab:baseline} reports OLS estimates of post-filing
annualised volatility on progressively richer sets of financial controls,
with two-digit SIC industry and fiscal-year fixed effects absorbed in all
specifications and standard errors clustered at the firm level.

\input{tables/baseline_regression}

\paragraph{Volatility persistence.}
Column~(1) includes only lagged volatility ($\sigma_{i,t}$) alongside the
fixed effects.  Its coefficient of $0.67$ ($t = 32.5$) confirms the
well-documented persistence of firm-level return volatility: a one
percentage-point increase in last year's annualised volatility is
associated with roughly a two-thirds percentage-point increase in next
year's volatility.  Even this parsimonious specification, combined with
industry and year fixed effects, explains roughly 63\% of the variation
in post-filing volatility, indicating that the bulk of the predictable
component of volatility is mechanical.

\paragraph{Firm size and capital structure.}
Column~(2) adds firm size, measured as the natural logarithm of total
assets, and leverage, defined as total liabilities over total assets.
Size enters with a negative and highly significant coefficient
($-0.016$, $t = -7.3$): larger firms exhibit lower future volatility,
consistent with the well-documented size--risk relation
\parencite{campbell2014}.  Leverage is economically negligible and
statistically insignificant ($t = 0.08$), likely because the
industry fixed effects already absorb much of the cross-sectional
variation in capital structure.

\paragraph{Profitability, growth, and earnings quality.}
The full specification in Column~(3) adds return on assets, asset
growth, and accruals.  ROA carries a large negative coefficient
($-0.240$, $t = -6.8$): more profitable firms face lower future
volatility.  Asset growth enters positively ($+0.027$, $t = 3.4$),
suggesting that rapid expansion is associated with higher subsequent
uncertainty.

Accruals, defined as $(\text{NI} - \text{OCF}) / \text{Total Assets}$,
enter with a positive but statistically insignificant coefficient
($0.057$, $t = 1.2$).  The overlap with ROA ($r = 0.44$) likely
absorbs most of its standalone predictive content.  Accruals are
retained because they serve a role in the subsequent divergence
analysis (Hypothesis~3).

The incremental adjusted~$R^2$ from these three
variables is modest (0.653 vs.\ 0.642), indicating that profitability,
growth, and earnings quality refine the prediction beyond what size and
past volatility already capture, but do not dominate it.

\paragraph{Benchmark for textual analysis.}
The full baseline model explains 65.3\% of the variation in post-filing
volatility.  This adjusted~$R^2$ serves as the benchmark against which
subsequent models---augmented with textual features and the divergence
measure---will be evaluated.  Any incremental explanatory power from
narrative disclosures must exceed this already high bar, which is
consistent with the view that financial-statement variables and
volatility persistence jointly account for the majority of predictable
firm-level risk.
